---
title: "Untitled"
author: "alex jack"
date: "2024-02-02"
output: html_document
---
```{r, load packages}
library("rgdal")
library("raster")
library("sf")
library("leafsync")
library(stars)
library("ggplot2")
library("stars")
library(XML)
library(spatialEco)
library(spatstat.random)
library(landscapemetrics)
library(maps)
library(reshape2)
library(reshape)
library(exifr)
library(gtools)
library(dplyr)
library(jsonlite)
library(stringr)
library(scales)
library(ggrepel)
library(landscapemetrics)
```
```{r, load data create global constants}

imgDatf<-read.table(
  "./data/imgDatf.csv",
  sep=",", header=TRUE)
imgDatw<-read.table(
  "./data/imgDatw.csv",
  sep=",", header=TRUE)
imgDats<-read.table(
  "./data/imgDats.csv",
  sep=",", header=TRUE)
imgDats <- imgDatf[,-c(which(colnames(imgDatf)=="deerSex"))]
imgDat<-imgDats
```
```{r helper functions}
splitJPGS <- function(dataframe, uidName){
  for(i in 1:nrow(dataframe)){
  # strip away the .JPG suffix; if there is one
  if(grepl(".JPG", dataframe[i,uidName])){
    dataframe[i,uidName] <- strsplit(dataframe[i,uidName], "\\.")[[1]][1]
  }
  }
  return(dataframe)
}
```

```{r}
imgDat$imgID <- toupper(imgDat$imgID)
imgDat <- imgDat %>% filter(grepl("S05",imgID))

imgDat$season <- 0
imgDat$site <- 0
imgDat$cam <- 0
imgDat$imgNum <- 0
imgDat$num <- 0
#imgDat <- imgDat %>% dplyr::select(imgID, season, site, cam, imgNum, numInds, class, loc, spcs, notes)
imgDat <- imgDat %>% filter(!(class== "deer" & loc== "I")) %>% filter(class!="bird")
for(i in 1:nrow(imgDat)){
  if(grepl(".JPG",imgDat[i,]$imgID)){
      imgID<-strsplit(imgDat[i,]$imgID, "\\.")[[1]][1]
      uidStringArr <- strsplit(imgID, "-")[[1]]
  }else{
      uidStringArr <- strsplit(imgDat[i,]$imgID, "-")[[1]]
  }
  imgDat[i,]$season <- uidStringArr[1]
  imgDat[i,]$site <- uidStringArr[2]
  imgDat[i,]$cam <- uidStringArr[3]
  imgDat[i,]$imgNum <- as.integer(uidStringArr[4])
}

```

```{r, summarise imgDatf}

imgDat$spcs <- tolower(imgDat$spcs)
for(i in 1:nrow(imgDat)){
  if(imgDat[i,]$spcs == "great horned owl"){
    imgDat[i,]$spcs <- "great-horned owl"
  }
  if(imgDat[i,]$spcs == "raccooon"){
    imgDat[i,]$spcs <- "raccoon"
  }
  if(imgDat[i,]$spcs == "cat"){
    imgDat[i,]$spcs <- "domestic cat"
  }
  if(imgDat[i,]$spcs == "dog"){
    imgDatf[i,]$spcs <- "domestic dog"
  }
  if(imgDat[i,]$class == "deer"){
    imgDat[i,]$spcs <- "white-tailed deer"
  }
  if(imgDat[i,]$class == "hawk"){
    imgDat[i,]$spcs <- "unknown hawk spp."
  }
}


imgDat <- imgDat %>% filter(!(spcs %in% c("cottontail", " grey squirrel", "chipmunk", "cow", "13 lined groundsquirrel", "grey squirrel")))
for(i in 1:nrow(imgDat)){
  if(imgDat[i,]$class == "meso-carn" || imgDat[i,]$class == "small-mam" || imgDat[i,]$class == "carnivore"){
    imgDat[i,]$class <- "furbearer"
  }
}

imgDat$deployString = paste0(imgDat$season, "-", imgDat$site, "-", imgDat$cam)

imgDatIndEnct <- imgDat[which(imgDat$sequenceID != 0),]


```{r setup, include=FALSE}
# clean species tags
# remove capital letters
imgDatspcs <- imgDatIndEnct %>% filter(!duplicated(deployString, sequenceID))
imgDatspcsGrouped <- imgDatIndEnct %>% mutate(deployStringSequence = paste0(deployString, "-", sequenceID))
imgDatspcsGroupedU <- data.frame(matrix(NA, ncol=ncol(imgDatspcsGrouped), nrow=0))
names(imgDatspcsGroupedU) <- names(imgDatspcsGrouped)
deployStringSequences <- unique(imgDatspcsGrouped$deployStringSequence)
for(i in 1:length(deployStringSequences)){
 sequence <- imgDatspcsGrouped[which(imgDatspcsGrouped$deployStringSequence == deployStringSequences[i]),]
 if(any(sequence$spcs != "white-tailed deer")){
   imgDatspcsGroupedU[i,] <- sequence[1,]
   #imgDatspcsGroupedU[i,]$numInds <- mean(sequence$numInds, na.rm=TRUE)

 }
 if(any(sequence$spcs == "white-tailed deer")){
    if(all(sequence$contactPossible == FALSE) & all(sequence$contactSeen == FALSE)){
      imgDatspcsGroupedU[i,] <- sequence[1,]
      #print(sequence[1,])
      # if(!is.na(sequence$numInds)){
      #   
      # }
      # imgDatspcsGrouped[i,]$numInds <- mean(sequence$numInds, na.rm=TRUE)
    }
     if(any(sequence$contactPossible == TRUE) & all(sequence$contactSeen == FALSE)){
       contact <- sequence[which(sequence$contactPossible==TRUE),]
       imgDatspcsGroupedU[i,] <- contact[1,] # grab the first entry
       #print(contact[1,])
       #imgDatspcsGroupedU[i,]$numInds <- mean(sequence$numInds, na.rm=TRUE)
     }
   if(any(sequence$contactSeen == TRUE)){
       contact <- sequence[which(sequence$contactPossible==TRUE),]
       imgDatspcsGroupedU[i,] <- contact[1,] # grab the first entry
       #imgDatspcsGroupedU[i,]$numInds <- mean(sequence$numInds, na.rm=TRUE)
      }
 }
}
imgDatspcsMeta <- imgDatspcsGroupedU
imgDatspcsMeta <- imgDatspcsMeta %>% dplyr::select(spcs)
write.table(imgDatspcsGroupedU, "./S05-unique-grouped")
write.table(imgDat, "./S05-complete")
write.table(imgDatIndEnct, "./S05-independent-seq")
write.table(imgDatspcsMeta, "./S05-spcs-meta")

```
