---
title: "S05-Summary"
output:
  pdf_document: default
  html_document: default
date: "2024-01-13"
---

```{r load packages, echo=FALSE}

suppressPackageStartupMessages({
    library(ggplot2)
    library(dplyr)
})


```
```{r read in data, echo=FALSE}
imgDatspcsMeta<-read.table("./S05-spcs-meta")
```
```{r summarise imgs by spcs,echo=FALSE}
ggplot(imgDatspcsMeta, aes(x=spcs)) +
  geom_bar() +
  ggtitle(label="Occurences of Species on Fier Farm")+
    theme(plot.title = element_text(hjust = 0.5), panel.background = element_blank(), axis.line=element_line(color="black", size = 0.5))
imgDatspcsMeta %>% group_by(spcs)%>% select(spcs) %>% summarise(n=n()) 

```
We collected 206,466 images. I counted any sighting of different species as unique observations and any sightings of the same species after a period of 30 minutes as unique observations. Of 42 unique observations of White-tailed deer I found that 5 of them had the potential to be instances where direct contact between wild deer and your farmed deer occurred. Due to objects obstructing my viewshed of my cameras I was unable to determine if contact occurred. 
